---
  title: "Coding Assignment 3"
author: "Team 15"
date: "Due: 2023-12-09 23:59"
output: 
  pdf_document:
  toc: true
---

  ```{r setup, include=FALSE}
#Put any packages you need here
library(tidyverse)
library(lmtest)
library(readxl)
library(plotly)
library(corrplot)
library(dplyr) # for pipe operator
library(gt) # for fancier tables
library(gtsummary) # for fancier summary statistics
library(corrplot) # for fancier correlations
library(car) # for easier scatterplots
library(jtools) # for fancier regression output
knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 100 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 100 customers in the sample is as follows:
  
  -	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=TRUE}
# Bring in the dataset here.
read.csv("~/Documents/Insurance_Data_Group15.csv")
```

## Question 1

Randomly select 30 observations from the sample and exclude from all modeling (i.e. n=47). Provide the summary statistics (min, max, std, mean, median) of the quantitative variables for the 70 observations.

```{r q1}
#
set.seed(123457)
index <- sample(seq_len(nrow(Insurance_Data_Group15)), size = 30)
Sample <- Insurance_Data_Group15[-index,]
Else <- Insurance_Data_Group15[index,]
Quantatative <- Sample[, c("Age", "BMI", "Children")]
summary(Quantatative)
Standard_Deviation_Age <- sd(Sample$Age)
Standard_Deviation_BMI <- sd(Sample$BMI)
Standard_Deviation_Children <- sd(Sample$Children)
print(Standard_Deviation_BMI)
print(Standard_Deviation_Age)
print(Standard_Deviation_Children)
```


## Question 2

Provide the correlation between all quantitative variables
```{r}
Quantatative <- Sample[, c("Age", "BMI", "Children")]
correlation_matrix <- cor(Quantatative)
print(correlation_matrix)
```
## Question 3
Run a regression that includes all independent variables in the data table. Does the model above violate any of the Gauss-Markov assumptions? If so, what are they and what is the solution for correcting?
```{r q4}
library(car)
library(lmtest)
library(plotly)
library(gtsummary)
#Linear Regression for all independent variables
Model_All_Variables <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = Sample)
summary(Model_All_Variables)
par(mfrow=c(2,2))
plot(Model_All_Variables)
``` 
## Results
Based on the plot titled "Residuals vs Fitted", it would appear as if there is a pattern.

In the second plot, "Normal Q-Q", you see the assumption of uniformly distributed set of residuals. Since it deviates from the line, we know this assumption is violated

"Scale-Location" plot should yield fairly consistent points around a horizontal line. This, indeed, seems to be the case. Hence, this assumption has not been violated.

## Question 4
  
  Implement the solutions from question 3, such as data transformation, along with any other changes you wish. Use the sample data and run a new regression. How have the fit measures changed? How have the signs and significance of the coefficients changed?
  
```{r q4}
#BMI
par(mfrow=c(1,2))
hist(Quantatative$BMI) #Before
Quantatative$lnBMI <- log(Quantatative$BMI)
hist(Quantatative$lnBMI) #After
#Age
par(mfrow=c(1,2))
hist(Quantatative$Age) #Before
Quantatative$lnAge <- log(Quantatative$Age)
hist(Quantatative$lnAge) #After
#Transforming Just BMI
Model_All_Variables_BMI_Transformed <- lm(Charges ~ Age + Quantatative$lnBMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = Sample)
summary(Model_All_Variables_BMI_Transformed)
#Transforming Age and BMI
Model_All_Variables_Both_Transformed <- lm(Charges ~ Quantatative$lnAge + Quantatative$lnBMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = Sample)
summary(Model_All_Variables_Both_Transformed)
```
## Answer
We are running a natural logarithm on BMI and Age since those are the things that would intuitively put more stress on the healthcare system and result in more frequent visits to a PCP

Running a natural log on BMI results in a more normally distributed set of values per histogram. Running a natural log on Age did not seem to do much for the distribution. Went from fairly normal to more normal. 

For the regression, we ran two models: one in which we only transform BMI, since it had the bigger change in distribution per the histograms and then a model of both BMI and Age transformed. 

Original: R^2 = 0.7598

Just BMI: better fit than original. No coefficient sign changes of variables that tested significant on 2-tailed test . R^2 = 0.7604

BMI and Age: worse fit than original by a litlte bit. Also no coefficient sign changes of variables that tested significant on 2 tailed test. R^2 = 0.74



## Question 5

Use the 30 withheld observations and calculate the performance measures for your best two models. Which is the better model? (remember that "better" depends on whether your outlook is short or long run)

```{r q5}
#
```


## Question 6

Provide interpretations of the coefficients, do the signs make sense? Perform marginal change analysis (thing 2) on the independent variables.

```{r}
#
```

## Question 7

An eager insurance representative comes back with five potential clients. Using the better of the two models selected above, provide the prediction intervals for the five potential clients using the information provided by the insurance rep.

| Customer | Age | BMI | Female | Children | Smoker | City           |
  | -------- | --- | --- | ------ | -------- | ------ | -------------- | 
  | 1        | 60  | 22  | 1      | 0        | 0      | Oviedo         |
  | 2        | 40  | 30  | 0      | 1        | 0      | Sanford        |
  | 3        | 25  | 25  | 0      | 0        | 1      | Winter Park    |
  | 4        | 33  | 35  | 1      | 2        | 0      | Winter Springs |
  | 5        | 45  | 27  | 1      | 3        | 0      | Oviedo         |
  
  
  ```{r}
#
```

## Question 8

The owner notices that some of the predictions are wider than others, explain why.

## Question 9 

Are there any prediction problems that occur with the five potential clients? If so, explain.