---
title: "Coding Assignment 2"
author: "Team 15"
date: "Due: 2023-10-22 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(plotly)
library(corrplot)
library(dplyr) # for pipe operator
library(gt) # for fancier tables
library(gtsummary) # for fancier summary statistics
library(corrplot) # for fancier correlations
library(car) # for easier scatterplots
library(jtools) # for fancier regression output

knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 100 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 100 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/Insurance_Data_Group15.csv")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$
charges = -7961.05 + 239.58*Age + 191.67*BMI + 732.97*Children + -1273.75*Female + 24367.51*Smoker + 1532.91*WinterSprings + 2052.98*WinterPark + -1238.64*Oviedo

```{r q1}
model <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = Insurance_Data_Group15)
summary(model)

charges <- -7961.05 + 239.58 + 191.67 + 732.97 + -1273.75 + 24367.51 + 1532.91 + 2052.98 + -1238.64


```
```{r}

summ(model)
tbl_regression(model)

```
Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$


## Question 2

Interpret the coefficients of all the independent variables that tested significant.

Age - Significant
BMI - Significant
Children - Not significant
Female - Not significant
Smoker - Significant
Winter Springs - Not significant
Winter Park - Not significant
Oviedo - Not significant

## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

```{r q3}

newPrediction <- data.frame(Age = 35, BMI = 26, Children = 1, Female = 1, Smoker = 0, Sanford = 1, WinterSprings = 0, WinterPark = 0, Oviedo = 0)

predict(model, newdata = newPrediction, interval = "confidence", level = .95)

```
Our prediction is that the amount of medical expenses associated with this policy is $4866.82

## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$

```{r q4}


```



